User Timeline Comparisons
========================================================

```{r imports_and_custom_funcs, echo=FALSE, results=FALSE}
library(ggplot2)
library(scales)

#Static Dates:
zone_a_ordered <- as.POSIXct(strptime("2012-10-28 07:00:00", "%Y-%m-%d %H:%M:%S"), tz="EST")


get_ggplot <-function (user) {
  data <- user
  data$TimeConvert <- as.POSIXct(strptime(data$Time, "%Y-%m-%d %H:%M:%S %z"), tz="EST")
  data$Time <- as.POSIXct(data$TimeConvert)
  
  plot <- ggplot(data, aes(x=Time, y=Action))
  
  if (!(length(unique(data$Sentiment))==1 & is.na(unique(data$Sentiment)))){
    plot <- plot + geom_text( aes( y = rep(c(60,61,62,63,64,65,66,67,68,69),1500), 
            label = Sentiment,   col=Sentiment),   size=3.5, vjust=-1, angle=10)
    }
  if (!unique(length(unique(data$Preparation))==1 & is.na(unique(data$Preparation)))){
    plot <- plot + geom_text( aes( y = rep(c(50,51,52,53,54,55,56,57,58,59),1500), 
            label = Preparation, col=Preparation), size=3.5, vjust=-1, angle=10)
    }
  if (!unique(length(unique(data$Environment))==1 & is.na(unique(data$Environment)))){
    plot <- plot + geom_text( aes( y = rep(c(30,31,32,33,34,35,36,37,38,39),1500), 
            label = Environment, col=Environment), size=3.5, vjust=-1, angle=10)
    }
  if (!unique(length(unique(data$Collective.Information))==1 & is.na(unique(data$Collective.Information)))){
    plot <- plot + geom_text( aes( y = rep(c(40,41,42,43,44,45,46,47,48,49),1500), 
            label=Collective.Information, col=Collective.Information), size=3.5, vjust=-1, angle=10)
    }
  if (!unique(length(unique(data$Movement))==1 & is.na(unique(data$Movement)))){
    plot <- plot + geom_text( aes( y = rep(c(20,21,22,23,24,25,26,27,28,29),1500),   
            label = Movement,    col=Movement),    size=3.5, vjust=-1, angle=10)
    }
    
  if (!unique(length(unique(data$Cluster))==1 & is.na(unique(data$Cluster)))){
    plot <- plot + geom_point( aes (y = Cluster, col = "Geo Location"))
    }
  
  #Add static data:
    plot <- plot + geom_vline(xintercept=as.numeric(zone_a_ordered), linetype="dotted", label="Evacuation Ordered")
  
  #House keeping:
    plot <- plot + theme(legend.position="none") +
                  scale_y_discrete(breaks=c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20,30,40,50,60,69), 
                                   labels=c("0","1","2","3","4","5","6","7","8","9","10","11","12","13","14","15","16","17","18","19",
                                          "Geo Location", "Reported Movement", "Environment","Collective Information", 
                                          "Preparation", "Sentiment"))
                                   
                                  

  return (plot)
}

```

##dogukanbiyik
```{r original_dogukanbiyik, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/dogukanbiyik_norm_distances.csv")
get_ggplot(data)
```

##kimdelcarmen
```{r original_kimdelcarmen, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/kimdelcarmen_norm_distances.csv")
get_ggplot(data)
```

##rchieB
```{r original_rchieB, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/rchieB_norm_distances.csv")
get_ggplot(data)
```

##fernanjos
```{r original_fernanjos, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/fernanjos_norm_distances.csv")
get_ggplot(data)
```

##nicolelmancini
```{r original_nicolelmancini, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/nicolelmancini_norm_distances.csv")
get_ggplot(data)
```

##Krazysoto
```{r original_Krazysoto, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/Krazysoto_norm_distances.csv")
get_ggplot(data)
```

##alishbot
```{r original_alishbot, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/alishbot_norm_distances.csv")
get_ggplot(data)
```

##CharisseCrammer
```{r original_CharisseCrammer, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/CharisseCrammer_norm_distances.csv")
get_ggplot(data)
```

##jericajazz
```{r original_jericajazz, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/jericajazz_norm_distances.csv")
get_ggplot(data)
```

##KD804
```{r original_KD804, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/KD804_norm_distances.csv")
get_ggplot(data)
```

##jesssgilligan
```{r original_jesssgilligan, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/jesssgilligan_norm_distances.csv")
get_ggplot(data)
```

##theJKinz
```{r original_theJKinz, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/theJKinz_norm_distances.csv")
get_ggplot(data)
```

##TheAwesomeMom
```{r original_TheAwesomeMom, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/TheAwesomeMom_norm_distances.csv")
get_ggplot(data)
```

##bjacksrevenge
```{r original_bjacksrevenge, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/bjacksrevenge_norm_distances.csv")
get_ggplot(data)
```

##jefflac
```{r original_jefflac, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/jefflac_norm_distances.csv")
get_ggplot(data)
```

##roobs83
```{r original_roobs83, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/roobs83_norm_distances.csv")
get_ggplot(data)
```

##jds2001
```{r original_jds2001, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/jds2001_norm_distances.csv")
get_ggplot(data)
```

##SimoMarms
```{r original_SimoMarms, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/SimoMarms_norm_distances.csv")
get_ggplot(data)
```

##NYCGreenmarkets
```{r original_NYCGreenmarkets, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/NYCGreenmarkets_norm_distances.csv")
get_ggplot(data)
```

##MoazaMatar
```{r original_MoazaMatar, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/MoazaMatar_norm_distances.csv")
get_ggplot(data)
```

##c3nki
```{r original_c3nki, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/c3nki_norm_distances.csv")
get_ggplot(data)
```

##KiiddPhenom
```{r original_KiiddPhenom, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/KiiddPhenom_norm_distances.csv")
get_ggplot(data)
```

##sandelestepan
```{r original_sandelestepan, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/sandelestepan_norm_distances.csv")
get_ggplot(data)
```

##tlal2
```{r original_tlal2, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/tlal2_norm_distances.csv")
get_ggplot(data)
```

##BeachyIsPeachy
```{r original_BeachyIsPeachy, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/BeachyIsPeachy_norm_distances.csv")
get_ggplot(data)
```

##cyantifik
```{r original_cyantifik, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/cyantifik_norm_distances.csv")
get_ggplot(data)
```

##FrankKnuck
```{r original_FrankKnuck, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/FrankKnuck_norm_distances.csv")
get_ggplot(data)
```

##mattgunn
```{r original_mattgunn, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/mattgunn_norm_distances.csv")
get_ggplot(data)
```

##Max_Not_Mark
```{r original_Max_Not_Mark, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/Max_Not_Mark_norm_distances.csv")
get_ggplot(data)
```

##JaclynPatrice
```{r original_JaclynPatrice, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/JaclynPatrice_norm_distances.csv")
get_ggplot(data)
```

##Rigo7x
```{r original_Rigo7x, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/Rigo7x_norm_distances.csv")
get_ggplot(data)
```

##ajc6789
```{r original_ajc6789, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/ajc6789_norm_distances.csv")
get_ggplot(data)
```

##yagoSMASH
```{r original_yagoSMASH, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/yagoSMASH_norm_distances.csv")
get_ggplot(data)
```

##polinchock
```{r original_polinchock, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/polinchock_norm_distances.csv")
get_ggplot(data)
```

##indavewetrust
```{r original_indavewetrust, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/indavewetrust_norm_distances.csv")
get_ggplot(data)
```

##CillaCindaplc2B
```{r original_CillaCindaplc2B, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/CillaCindaplc2B_norm_distances.csv")
get_ggplot(data)
```

##Javy_Jaz
```{r original_Javy_Jaz, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/Javy_Jaz_norm_distances.csv")
get_ggplot(data)
```

##eric13000
```{r original_eric13000, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/eric13000_norm_distances.csv")
get_ggplot(data)
```

##becaubs
```{r original_becaubs, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/becaubs_norm_distances.csv")
get_ggplot(data)
```

##enriqueskincare
```{r original_enriqueskincare, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/enriqueskincare_norm_distances.csv")
get_ggplot(data)
```

##Rivkind
```{r original_Rivkind, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/Rivkind_norm_distances.csv")
get_ggplot(data)
```

##janelles__world
```{r original_janelles__world, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/janelles__world_norm_distances.csv")
get_ggplot(data)
```

##CoreyKelly
```{r original_CoreyKelly, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/CoreyKelly_norm_distances.csv")
get_ggplot(data)
```

##josalazas
```{r original_josalazas, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/josalazas_norm_distances.csv")
get_ggplot(data)
```

##CapponiWho
```{r original_CapponiWho, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/CapponiWho_norm_distances.csv")
get_ggplot(data)
```

##JohnBakalian1
```{r original_JohnBakalian1, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/JohnBakalian1_norm_distances.csv")
get_ggplot(data)
```

##valcristdk
```{r original_valcristdk, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/valcristdk_norm_distances.csv")
get_ggplot(data)
```

##forero29
```{r original_forero29, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/forero29_norm_distances.csv")
get_ggplot(data)
```

##BobGrotz
```{r original_BobGrotz, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/BobGrotz_norm_distances.csv")
get_ggplot(data)
```

##CodyRodrigu3z
```{r original_CodyRodrigu3z, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/CodyRodrigu3z_norm_distances.csv")
get_ggplot(data)
```

##CoastalArtists
```{r original_CoastalArtists, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/CoastalArtists_norm_distances.csv")
get_ggplot(data)
```

##VSindha
```{r original_VSindha, echo=FALSE, warning=FALSE, fig.width=16, fig.height=8}
data = read.csv("../exports_3/VSindha_norm_distances.csv")
get_ggplot(data)
```